### 2016-05-12 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Minor edits to hose stream and gas burner reports

\large
\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (February 2016) \\
% http://dx.doi.org/10.6028/NIST.TN.XXXX \\
CODEN: NTNOEF }

@@

@@

\section{East Structure Tests}
\label{sec:east_procedure}
Five different tests---Tests 2, 3, 4, 5, and 6---were conducted in the East Structure. Tests~2--4 followed an identical order of events. Fig.~\ref{fig:Tests_2-4_layout} includes a floor plan schematic and table of event times corresponding to the data files for Tests~2--4. The procedures for Test~5 and Test~6 are outlined in a similar manner in Fig.~\ref{fig:east_test_5} and Fig.~\ref{fig:east_test_6}, respectively. Tests~5 and 6 involved performing a specific set of events three times sequentially. To avoid repetition of identical actions in the event time table, each set of events has been denoted as a ``sequence'' (abbreviated as ``seq.'' in the table). Additionally, Table~\ref{table:HRR_East} lists the calculated heat release rate for each test and sequence.

\begin{table}[!ht]
\caption{Calculated Heat Release Rate for East Structure Tests}
\begin{tabular}{lccccc}
 \toprule
 					& 	\multicolumn{5}{c}{\textbf{Heat Release Rate (kW)}} \\
\textbf{Test} 		&	\begin{tabular}{c} Corner \\ Burner On \end{tabular} 
					&	\begin{tabular}{c} Middle \\ Burner On \end{tabular}
					&	\begin{tabular}{c} Center \\ Burner On \end{tabular}
					& 	\begin{tabular}{c} Center \\ Burner Off \end{tabular}
					&   \begin{tabular}{c} Middle \\ Burner Off \end{tabular} \\
 \midrule
Test 2 				& 338 & 651	& 894 & 634 & 330 \\
Test 3				& 326 & 650	& 899 & 631 & 326 \\
Test 4				& 351 & 654	& 902 & 652 & 337 \\
Test 5 - Seq. 1		& 263 & 526	& 723 & 486 & 263 \\
Test 5 - Seq. 2		& 225 & 526	& 727 & 526 & 316 \\
Test 5 - Seq. 3		& 263 & 526	& 722 & 526 & 263 \\
Test 6 - Seq. 1		& 263 & 526	& 722 & 526 & 263 \\
Test 6 - Seq. 2		& 225 & 526	& 718 & 526 & 287 \\
Test 6 - Seq. 3		& 263 & 526	& 714 & N/A & N/A \\
% \begin{tabular}{lc}
%  \toprule
% \textbf{Test}  		& 	\textbf{Heat Release Rate (kW)} \\
% \midrule
% Test 2 				& 			\\
% Test 3				& 			\\
% Test 4				& 	949		\\
% Test 5 - Seq. 1		&  	723		\\
% Test 5 - Seq. 2		&  	728		\\
% Test 5 - Seq. 3		&  	724	    \\
% Test 6 - Seq. 1		&  	718	    \\
% Test 6 - Seq. 2		&   714     \\
% Test 6 - Seq. 3		&   716	 	\\
\bottomrule
\end{tabular}
\label{table:HRR_East}
\end{table}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Tests~2--4 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Test 2} & \textbf{Test 3} & \textbf{Test 4} \\
	\midrule
	(1) Corner burner on 			& 	21:00		  &		4:00		&		4:00	  \\
	(2) Middle burner on 			&   24:00		  &		7:00		&		7:00	  \\
	(3) Center burner on 			&   27:00		  &	   10:00		&	   10:00	  \\
	(4) West double door opened 	&   28:00		  &    11:00		&	   11:00	  \\
	(5) East double door opened 	&   30:00		  &    13:00		&	   13:00	  \\
	(6) South exterior door opened 	&   31:00		  &    14:00		&	   14:00	  \\
	(7) Center burner off 			&   33:00		  &    17:00		&	   17:00	  \\
	(8) Middle burner off 			&   35:00		  &    19:00		&	   19:00	  \\
	(9) Corner burner off 			&   37:00		  &    21:00		&	   21:00	  \\
	\bottomrule
	\end{tabular}
	\\~\\
	\textit{We ran a PPV fan after each test, but I didn't include it because the burners were off at the time. I can include this event if you would like, however. Unlike Tests 5 and 6, we did not ignite the burners again after running the PPV fan.}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_4}
\end{minipage}
\caption{Tests~2-4 layout and event times.}
\label{fig:Tests_2-4_layout}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~5 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	(1)  Corner burner on 			&	3:15	&	12:45	&	21:15	\\
	(2)  Middle burner on 			&	3:30	&	13:00	&	21:30	\\
	(3)  Center burner on 			&	3:45	&	13:15	&	21:45	\\
	(4)  West double door opened 	&	5:15	&   14:45	&	23:15	\\
	(5)  Roof vent opened 			&	6:45	&	15:45 	&	24:45 	\\
	(6)  Center burner off 		 	&	8:15	&   17:15	&	\multirow{3}{*}{Gas killed at truck (26:15)} \\
	(7)  Middle burner off		 	&	8:30	&   17:30	&	\\
	(8)  Corner burner off 			&	8:45	&   17:45	&	\\
	(9)  East double door opened	&	9:30	&   18:30	&	27:25	\\
	(10) Roof vent closed 			&	11:35	&   20:11	&	N/A		\\
	(11) East double door closed	&	12:02 	&	20:24	&	N/A 	\\
	(12) West double door closed	&	12:18 	&	20:41	&	N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
\end{minipage}
\caption{Test~5 layout and event times.}
\label{fig:east_test_5}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~6 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	(1) Corner burner on 			& 	14:00		  &	   34:30		&	   54:30	\\
	(2) Middle burner on 			&   14:15		  &	   34:45		&	   54:45	\\
	(3) Center burner on 			&   14:30		  &	   35:00		&	   55:00	\\
	(4) Roof vent opened 			&   16:38		  &    36:30		&	   56:30	\\
	(5) West double door opened 	&	17:03		  &	   38:00 		&	   58:00 	\\
	(6) East double door opened 	&   20:03		  &    39:30		&	   59:31	\\
	(7) Roof vent closed		 	&   21:30		  &    42:45		&	   61:43	\\
	(7) Center burner off 			&   23:00		  &    44:15		&	   63:30	\\
	(8) Middle burner off 			&   23:20		  &    44:30		&	   63:45	\\
	(9) Corner burner off 			&   23:40		  &    44:45		&	   64:00	\\
	(10) Roof vent opened			& 	26:05 		  &	   45:30		&	   65:30	\\
	(11) East double door closed	& 	33:17 		  &	   52:38		&	   N/A		\\
	(12) West double door closed	& 	33:30 		  &	   52:55		&	   N/A		\\
	(13) Roof vent closed		 	&   33:45		  &    53:54		&	   N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_6}
\end{minipage}
\caption{Test~6 layout and event times.}
\label{fig:east_test_6}
\end{figure}
\FloatBarrier

@@

\begin{table}[!ht]
\caption{Calculated Heat Release Rate for West Structure Tests}
% \begin{tabular}{lc}
%  \toprule
% \textbf{Test}  			& 	\begin{tabular}{c} \textbf{Heat Release Rate} \\ \textbf{(kW)} \end{tabular} \\
% \midrule
% Test 22 				& 	756		\\
% Test 23					& 	788		\\
% Test 24					& 	784		\\
% Test 25					&  	785		\\
\begin{tabular}{lccc}
 \toprule
 					& 	\multicolumn{3}{c}{\textbf{Heat Release Rate (kW)}} \\
\textbf{Test} 		& 	1 Burner On 	& 	2 Burners On 	& 	3 Burners On \\
 \midrule
Test 22				& 	  287		 	&      316			&     	759 	  \\
Test 23				& 	  395		 	&      526			&     	788 	  \\
Test 24				& 	  287		 	&      631			&     	787 	  \\
Test 25				& 	  316		 	&      526			&     	785 	  \\
\bottomrule
\end{tabular}
\label{table:HRR_West}
\end{table}

\begin{figure}[!ht]
% \begin{minipage}[b]{0.8\columnwidth}
% 	\begin{flushleft}
% 	\small
% 	\begin{tabular}[b]{cc}
%  	\toprule
%  	\textbf{Number} & \textbf{Event Description} \\
%  	\midrule
%  	1-3  & Burners ignited \\
%  	4	 & 2nd floor west double door opened \\
%  	5 	 & 1st floor west double door opened \\
%  	6	 & 1st floor east double door opened \\
%  	7 	 & 2nd floor east double door opened \\
%  	8-10  & Burners extinguished \\
% 	\bottomrule
% 	\end{tabular}
% 	\end{flushleft}
% \end{minipage}
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{\normalsize Event Times (mm:ss) for Tests~22--23 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 		& \textbf{Test 22}	& \textbf{Test 23} \\
	\midrule
	(1) Corner burner on 					& 	9:05 			&	 3:45		\\
	(2) Middle burner on 					&   8:45	  		&	 3:55		\\
	(3) Center burner on 					&   8:15	  		&	 4:04		\\
	(4) 2nd floor west double door opened 	&   11:30	  		&    6:00		\\
	(5) 1st floor west double door opened 	&	13:30	  		&    8:02 	 	\\
	(6) 1st floor east double door opened 	&   15:45		  	&    10:00		\\
	(7) 2nd floor east double door opened	&   18:00		  	&    12:08		\\
	(8) PPV fan on 							&   19:10		  	&    14:01		\\
	(9) PPV fan off              			&   21:34		  	&    16:30		\\
	(8) Center burner off 					&   22:00		  	&    17:00		\\
	(9) Middle burner off 					&   22:00		  	&    17:00		\\
	(10) Corner burner off 					&   22:00		  	&    17:00		\\
	% doors were opened, fan was on after burners turned off
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=0.86\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=0.86\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Tests 22--23 layout and event times.}
\label{fig:west_test_22}
\end{figure}

\begin{figure}[!ht]
% \begin{minipage}[b]{0.8\columnwidth}
% 	\begin{flushleft}
% 	\small
% 	\begin{tabular}[b]{cc}
%  	\toprule
%  	\textbf{Number} & \textbf{Event Description} \\
%  	\midrule
%  	1-3  & Burners ignited \\
%  	4	 & Interior stairwell door opened \\
%  	5 	 & 1st floor west double door opened \\
%  	6	 & 2nd floor west double door opened \\
%  	7 	 & 2nd floor south exterior door opened \\
%  	8-10 & Burners extinguished \\
% 	\bottomrule
% 	\end{tabular}
% 	\end{flushleft}
% \end{minipage}
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{\normalsize Event Times (mm:ss) for Tests 24--25 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 24}	& \textbf{Test 25} \\
	\midrule
	(1) Corner burner on 						& 	2:30 			&	 2:00		\\
	(2) Middle burner on 						&   2:45	  		&	 2:00		\\
	(3) Center burner on 						&   3:00	  		&	 2:00		\\
	(4) Interior stairwell door opened 			&   5:00	  		&    4:00		\\
	(5) 1st floor west double door opened 		&	7:00	  		&    6:11 	 	\\
	(6) 2nd floor west double door opened 		&   9:00		  	&    8:00		\\
	(7) 2nd floor south exterior door opened	&   11:00		  	&    10:00		\\
	(8) PPV fan on 								&   13:00		  	&    12:00 		\\
	% (9) PPV fan off              				&   16:30		  	&    		\\
	(8) Center burner off 						&   15:00		  	&    14:00		\\
	(9) Middle burner off 						&   15:00		  	&    14:00		\\
	(10) Corner burner off 						&   15:00		  	&    14:00		\\
	% doors were opened, fan was on after burners turned off
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=0.94\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
	\includegraphics[width=0.94\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
\end{minipage}
\caption{Tests 24--25 layout and event times.}
\label{fig:west_test_24}
\end{figure}
\FloatBarrier

>>>>

\large
\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (May 2016) \\
% http://dx.doi.org/10.6028/NIST.TN.XXXX \\
CODEN: NTNOEF }

@@

\subsubsection{Gas Flow Meter}

@@

\section{East Structure Tests}
\label{sec:east_procedure}
Five different tests, Tests 2--6, were conducted in the East Structure. Tests~2--4 followed an identical order of events. Fig.~\ref{fig:Tests_2-4_layout} includes a floor plan schematic and table of event times corresponding to the data files for Tests~2--4. The procedures for Test~5 and Test~6 are outlined in a similar manner in Fig.~\ref{fig:east_test_5} and Fig.~\ref{fig:east_test_6}, respectively. Tests~5 and 6 involved performing a specific set of events three times sequentially. To avoid repetition of identical actions in the event time table, each set of events has been denoted as a ``sequence'' (abbreviated as ``seq.'' in the table). Additionally, Table~\ref{table:HRR_East} lists the calculated heat release rate for each test and sequence.

\begin{table}[!ht]
\caption{Calculated Heat Release Rate for East Structure Tests}
\begin{tabular}{lccccc}
 \toprule
 					& 	\multicolumn{5}{c}{\textbf{Heat Release Rate (kW)}} \\
\textbf{Test} 		&	\begin{tabular}{c} Corner \\ Burner On \end{tabular} 
					&	\begin{tabular}{c} Middle \\ Burner On \end{tabular}
					&	\begin{tabular}{c} Center \\ Burner On \end{tabular}
					& 	\begin{tabular}{c} Center \\ Burner Off \end{tabular}
					&   \begin{tabular}{c} Middle \\ Burner Off \end{tabular} \\
 \midrule
Test 2 				& 338 & 651	& 894 & 634 & 330 \\
Test 3				& 326 & 650	& 899 & 631 & 326 \\
Test 4				& 351 & 654	& 902 & 652 & 337 \\
Test 5 - Seq. 1		& 263 & 526	& 723 & 486 & 263 \\
Test 5 - Seq. 2		& 225 & 526	& 727 & 526 & 316 \\
Test 5 - Seq. 3		& 263 & 526	& 722 & 526 & 263 \\
Test 6 - Seq. 1		& 263 & 526	& 722 & 526 & 263 \\
Test 6 - Seq. 2		& 225 & 526	& 718 & 526 & 287 \\
Test 6 - Seq. 3		& 263 & 526	& 714 & N/A & N/A \\
\bottomrule
\end{tabular}
\label{table:HRR_East}
\end{table}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Tests~2--4 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Test 2} & \textbf{Test 3} & \textbf{Test 4} \\
	\midrule
	~(1)~ Corner burner on 				& 	21:00		  &		4:00		&		4:00	  \\
	~(2)~ Middle burner on 				&   24:00		  &		7:00		&		7:00	  \\
	~(3)~ Center burner on 				&   27:00		  &	   10:00		&	   10:00	  \\
	~(4)~ West double door opened 		&   28:00		  &    11:00		&	   11:00	  \\
	~(5)~ East double door opened 		&   30:00		  &    13:00		&	   13:00	  \\
	~(6)~ South exterior door opened 	&   31:00		  &    14:00		&	   14:00	  \\
	~(7)~ Center burner off				&   33:00		  &    17:00		&	   17:00	  \\
	~(8)~ Middle burner off				&   35:00		  &    19:00		&	   19:00	  \\
	~(9)~ Corner burner off				&   37:00		  &    21:00		&	   21:00	  \\
	(10) PPV fan on 					& 	42:01		  &    26:00		&  	   26:00	  \\	
	(11) PPV fan off 					& 	52:30 		  &    36:00  		&  	   36:00$^*$  \\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_4}
\end{minipage}
\caption{Tests~2-4 layout and event times.}
\label{fig:Tests_2-4_layout}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~5 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	% Some door(s) opened before test start according to notes, no sign from data/limited videos
	~(1)~ Corner burner on 			& 	14:00		  &	   34:30		&	   54:30	\\
	~(2)~ Middle burner on 			&   14:15		  &	   34:45		&	   54:45	\\
	~(3)~ Center burner on 			&   14:30		  &	   35:00		&	   55:00	\\
	~(4)~ Roof vent opened 			&   16:38		  &    36:30		&	   56:30	\\
	~(5)~ West double door opened 	&	17:03		  &	   38:00 		&	   58:00 	\\
	~(6)~ East double door opened 	&   20:03		  &    39:30		&	   59:31	\\
	~(7)~ Roof vent closed		 	&   21:30		  &    42:45		&	   61:43	\\
	~(7)~ Center burner off 		&   23:00		  &    44:15		&	   63:30	\\
	~(8)~ Middle burner off 		&   23:20		  &    44:30		&	   63:45	\\
	~(9)~ Corner burner off 		&   23:40		  &    44:45		&	   64:00	\\
	(10) Roof vent opened			& 	26:05 		  &	   45:30		&	   65:30	\\
	(11) East double door closed	& 	33:17 		  &	   52:38		&	   N/A		\\
	(12) West double door closed	& 	33:30 		  &	   52:55		&	   N/A		\\
	(13) Roof vent closed		 	&   33:45		  &    53:54		&	   N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
\end{minipage}
\caption{Test~5 layout and event times.}
\label{fig:east_test_5}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~6 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	~(1)~  Corner burner on 		&	3:15	&	12:45	&	21:15	\\
	~(2)~  Middle burner on 		&	3:30	&	13:00	&	21:30	\\
	~(3)~  Center burner on 		&	3:45	&	13:15	&	21:45	\\
	~(4)~  West double door opened 	&	5:15	&   14:45	&	23:15	\\
	~(5)~  Roof vent opened 		&	6:45	&	15:45 	&	24:45 	\\
	~(6)~  Center burner off 		&	8:15	&   17:15	&	\multirow{3}{*}{Gas killed at truck (26:15)} \\
	~(7)~  Middle burner off		&	8:30	&   17:30	&	\\
	~(8)~  Corner burner off 		&	8:45	&   17:45	&	\\
	~(9)~  East double door opened	&	9:30	&   18:30	&	27:25	\\
	(10) Roof vent closed 			&	11:35	&   20:41	&	N/A		\\
	(11) East double door closed	&	12:02 	&	20:11	&	N/A 	\\
	(12) West double door closed	&	12:18 	&	20:24	&	N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_6}
\end{minipage}
\caption{Test~6 layout and event times.}
\label{fig:east_test_6}
\end{figure}
\FloatBarrier

@@

\begin{table}[!ht]
\caption{Calculated Heat Release Rate for West Structure Tests}
% \begin{tabular}{lc}
%  \toprule
% \textbf{Test}  			& 	\begin{tabular}{c} \textbf{Heat Release Rate} \\ \textbf{(kW)} \end{tabular} \\
% \midrule
% Test 22 				& 	756		\\
% Test 23					& 	788		\\
% Test 24					& 	784		\\
% Test 25					&  	785		\\
\begin{tabular}{lccc}
 \toprule
 					& 	\multicolumn{3}{c}{\textbf{Heat Release Rate (kW)}} \\
\textbf{Test} 		& 	1 Burner On 	& 	2 Burners On 	& 	3 Burners On \\
 \midrule
Test 22				& 	  287		 	&      316			&     	759 	  \\
Test 23				& 	  395		 	&      526			&     	788 	  \\
Test 24				& 	  287		 	&      631			&     	787 	  \\
Test 25				& 	  N/A		 	&      N/A			&     	785 	  \\
\bottomrule
\end{tabular}
\label{table:HRR_West}
\end{table}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (mm:ss) for Tests~22--23 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 22}	& \textbf{Test 23} \\
	\midrule
	~(1)~  Corner burner on 					& 	9:05 			&	 3:45		\\
	~(2)~  Middle burner on 					&   8:45	  		&	 3:55		\\
	~(3)~  Center burner on 					&   8:15	  		&	 4:04		\\
	~(4)~  2nd floor west double door opened 	&   11:30	  		&    6:00		\\
	~(5)~  1st floor west double door opened 	&	13:30	  		&    8:02 	 	\\
	~(6)~  1st floor east double door opened 	&   15:45		  	&    10:00		\\
	~(7)~  2nd floor east double door opened	&   18:00		  	&    12:08		\\
	~(8)~  PPV fan on 							&   19:10		  	&    14:01		\\
	~(9)~  PPV fan off              			&   21:34		  	&    16:30		\\
	(10) All burners off 						&   22:00		  	&    17:00		\\
	(11) 2nd floor south exterior door opened 	&   23:19		  	&    18:01		\\
	(12) PPV fan on 	 						&   26:00		  	&    19:30		\\
	(13) 2nd floor south exterior door closed   &   27:56		  	&    N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=0.84\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=0.84\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Tests 22--23 layout and event times.}
\label{fig:west_test_22}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (mm:ss) for Tests 24--25 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 24}	& \textbf{Test 25} \\
	\midrule
	~(1)~ Corner burner on 						& 	2:30 			&	 2:00		\\
	~(2)~ Middle burner on 						&   2:45	  		&	 2:00		\\
	~(3)~ Center burner on 						&   3:00	  		&	 2:00		\\
	~(4)~ Interior stairwell door opened 		&   5:00	  		&    4:00		\\
	~(5)~ 1st floor west double door opened 	&	7:00	  		&    6:11 	 	\\
	~(6)~ 2nd floor west double door opened 	&   9:00		  	&    8:00		\\
	~(7)~ 2nd floor south exterior door opened	&   11:00		  	&    10:00		\\
	~(8)~ PPV fan on 							&   13:00		  	&    12:00 		\\
	~(9)~ All burners off 						&   15:00		  	&    14:00		\\
	(10) 2nd floor east double door opened 		&   17:15		  	&    16:00		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=0.94\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
	\includegraphics[width=0.94\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
\end{minipage}
\caption{Tests 24--25 layout and event times.}
\label{fig:west_test_24}
\end{figure}
\FloatBarrier
